\vspace{-15mm} \Large \textbf{Utilisation of Computer Algorithms in the Optimisation of Building Envelopes Thermal Performance}

### 2013-11-29 Paper.tex
Added Tabu Search (Friday, Nov 29th 2013)

@@

Cellular Automata is a computational method which can simulate complex growth systems using simple rules, the initial configuration would include at least one cell (Fig. \ref{fig:CellularAuto}).
\end{multicols}
\begin{Figure}
	\centering	
	\includegraphics[width=0.7\linewidth]{./Images/2-CellularAutomata}
	\captionof{figure}{An example of cellular automata showing (a) the sequence of generations and (b) the governing rule. \cite{wolfram02}}
	\label{fig:CellularAuto}
\end{Figure}

\begin{multicols}{2}
A Voronoi Diagram is a way of decomposing a space into regions, which is a process initiated with a set of points in space called generating points; then, lines are drawn from an equal distance from each two points, creating polygons or cells (Fig \ref{fig:Voronoi}).

\begin{Figure}
	\includegraphics[width=\linewidth]{./Images/3-VoronoiDiagram}
	\captionof{figure}{A Voronoi Diagram \cite{fujita00}}
	\label{fig:Voronoi}
\end{Figure}

@@

The general mathematical form of unconstrained optimisation is:\\
\begin{equation}
\text{Minimise:} f(x), x=[x_1,x_2\dots,x_n]^T \in \mathbb{R}
\end{equation}
The continuous components of $x$ are called the design variables, and $f(x)$ is the objective function. The optimum vector that solves the equation is denoted by \textbf{x*} with a corresponding optimum function value of $f(\text{\textbf{x*}})$ (Fig. \ref{fig:LocalOptimum}).

@@

\begin{Figure}
	\includegraphics[width=\linewidth]{./Images/4-LocalOptimum}
	\captionof{figure}{A single variable function with the optimum at \textbf{x*} \cite{snyman05}}
	\label{fig:LocalOptimum}
\end{Figure}

\end{multicols}
\begin{Figure}
	\centering	
	\includegraphics[width=0.8\linewidth]{./Images/5-OptimisationModel}
	\captionof{figure}{The Mathematical Optimisation Modelling Process \cite{snyman05}}
	\label{fig:OptimisationModel}
\end{Figure}
\begin{multicols}{2}

@@

Having explained the mathematical and basic programming concepts behind optimisation algorithms, the next step is to define the function in question; the \emph{objective function}. In this particular case the objective function is the thermal performance of building envelopes. The exchange of heat between the building and external environment is expressed in the following equation:
\begin{equation}
	Qi\pm Qc\pm Qs\pm Qv-Qe=\Delta S
\end{equation}
\footnotesize
\indent$Qi=$Internal heat gain\\
\indent$Qc=$Conduction heat gain or loss\\
\indent$Qs=$Solar heat gain\\
\indent$Qv=$Ventilation heat gain or loss\\
\indent$Qe=$Evaporation heat loss\\
\indent$\Delta S=$Difference in stored heat
\normalsize

>>>>

%------------------
% Code
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

@@

Out of the above, two examples are explained briefly here. Cellular Automata is a computational method which can simulate complex growth systems using simple rules, the initial configuration would include at least one cell (Fig. \ref{fig:CellularAuto}).

\begin{Figure}
	\centering	
	\includegraphics[width=\linewidth]{./Images/2-CellularAutomata}
	\captionof{figure}{An example of cellular automata showing (a) the sequence of generations and (b) the governing rule. \cite{wolfram02}}
	\label{fig:CellularAuto}
\end{Figure}

A Voronoi Diagram is a way of decomposing a space into regions, which is a process initiated with a set of points in space called generating points; then, lines are drawn from an equal distance from each two points, creating polygons or cells (Fig \ref{fig:Voronoi}).

\begin{Figure}
	\centering
	\includegraphics[width=0.8\linewidth]{./Images/3-VoronoiDiagram}
	\captionof{figure}{A Voronoi Diagram \cite{fujita00}}
	\label{fig:Voronoi}
\end{Figure}

@@

		The general mathematical form of unconstrained optimisation is:\\
\begin{equation}
\text{min} f(x), x=[x_1,x_2\dots,x_n]^T \in \mathbb{R}
\end{equation}
The continuous components of $x$ are called the design variables, and $f(x)$ is the objective function. The optimum vector that solves the equation is denoted by \textbf{x*} with a corresponding optimum function value of $f(\text{\textbf{x*}})$ (Fig. \ref{fig:LocalOptimum}).

@@

\end{multicols}
\begin{Figure}
	\centering
	\includegraphics[width=0.6\linewidth]{./Images/4-LocalOptimum}
	\captionof{figure}{A single variable function with the optimum at \textbf{x*} \cite{snyman05}}
	\label{fig:LocalOptimum}
\end{Figure}

\begin{Figure}
	\centering	
	\includegraphics[width=0.7\linewidth]{./Images/5-OptimisationModel}
	\captionof{figure}{The Mathematical Optimisation Modelling Process \cite{snyman05}}
	\label{fig:OptimisationModel}
\end{Figure}
\begin{multicols}{2}

	\paragraph{Types of Optimisation Algorithms}
	Mathematical optimisation algorithms are numerous and differ greatly in solution space searching methods. The predominantly common algorithms in architectural applications are:
	\begin{compactenum}
	\item Genetic Algorithm
	\item Simmulated Annaeling
	\item Tabu Search
	\end{compactenum}
	It should be noted that although the three are very different in terms of origin and search method, they have one thing in common which is being under the \emph{Metaheuristic}\footnote{\emph{Metaheuristic}: an algorithm which guides a heuristic (self learning) search method} class of mathematical optimisation algorithms.

	\subparagraph{Genetic Algorithm}

	Genetic Algorithms are \emph{evolutionary} algorithms which simulate biological evolution, and draws most of its terminology from biological evolutionary science.

	The process of optimisation using GA can be described as follows: ``Under GA terminology, a solution to a problem is an \emph{individual}, and the group of solutions existent at each stage is a \emph{population}. Each time a new population of individuals is created it is called a \emph{generation}. In binary GA's[\dots]each individual is represented by a binary string called \emph{chromosome}, which encodes all parameters of interest corresponding to that individual. A chromosome of formed of \emph{alleles}; the binary coding bits. The fitness of any particular individual corresponds to the value of the objective function at that point''. \cite{caldas01}

	An \emph{initial population} is randomly generated, with each of the individuals coded with different \emph{genetic} design variables (using the notion of chromosomes), then a number of stochastic operators start to manipulate the initial population, including \begin{inparaenum} \item \emph{crossovers}; the swapping of parts of chromosome values between different individuals, and \item \emph{mutation}; introducing new values randomly to some individuals to create diversity.\end{inparaenum}

	Finally an elitist model is created from the best set of solutions in this generation, and is used as the initial population of the next generation, and the same loop keeps repeating until the termination criteria of the GA are met and the final set of solutions are recorded (see Fig. \ref{fig:GA}).

	\begin{Figure}
		\centering
		\includegraphics[height=7cm]{./Images/6-GA}
		\captionof{figure}{Flowchart showing stages of GA}
		\label{fig:GA}
	\end{Figure}

	\subparagraph{Simmulated Annaeling}

	Simmulated Annaeling is as mathematical optimisation method. It draws its terminology from the metallurgical process of annealing which is the heating and controlled cooling of metals to reach its ground state with the lowest internal energy \cite{lam88}. This search method is also Metaheuristic, with emphasis on find the \emph{global} maximum or minimum. The process of Simmulated Annealing is described by the following algorithm (in pseudocode):\\

		\begin{algorithmic}[1]
			\State Get an initial state with energy $x$
			\State Make the initial state the current state
			\State Select an initial high temperature $T$
			\While {System is not yet frozen}
			\While {System is not yet in thermal equilibrium}
				\State pick a random nearby state with energy $x_p$
				\State let $\Delta x = x_p - x$
				\If {$\Delta x \leq 0$}
					\State the new state becomes the current state
				\Else
					\State reject state
				\EndIf
			\EndWhile
			\State Reduce the temperature $T$ by $\Delta T$
			\EndWhile
			\State Output the current state
		\end{algorithmic}

	\subparagraph{Tabu Search}

	Tabu Search depends on what are called \emph{adaptive memory} and {responsive expolration}. The basic principle is that it heavely uses different memory-based techniques to \begin{inparaenum} \item avoid revisiting previously tested solutions, \item to memorise elements that are common among good solutions, and \item the impact of choices made till a certain point on the progress of the search to find the optimum solution, which is an added level of self-learning.\end{inparaenum}

	This makes Tabu Search a very intelligent search method, which is very efficient at find the optimum solutions in large solution spaces, or to complex problems.

@@

Having explained the mathematical and basic programming concepts behind optimisation algorithms, the next step is to define the function in question; the \emph{objective function}. In this particular case the objective function is the thermal performance of building envelopes. The exchange of heat between the building and external environment is expressed in the following equation:
\begin{equation}
	Qi\pm Qc\pm Qs\pm Qv-Qe=\Delta S
\end{equation}
\footnotesize
\indent$Qi=$Internal heat gain\\
\indent$Qc=$Conduction heat gain or loss\\
\indent$Qs=$Solar heat gain\\
\indent$Qv=$Ventilation heat gain or loss\\
\indent$Qe=$Evaporation heat loss\\
\indent$\Delta S=$Difference in stored heat\\
\normalsize
